A Secondary Screen Architecture to Accurately Capture Viewers' Interactions in an iTV Environment

### 2014-06-04 src/paper.tex
WIP: Changes in introduction and architecture

\begin{abstract}
Advances in TV technology have enabled viewers to actively interact with the TV through interactive applications instead of just passively watching TV. Typically, a conventional remote control is shared by many viewers and it is difficult to accurately capture the individual interaction data from each viewer. It is also difficult to identify the context in which the interactions occur, e.g., to manage precisely who is present in the environment and what is being watched on TV. In this paper, it is presented a novel architecture that facilitates the capture of viewers' individual interactions and contextual data in shared TV environments. This architecture uses personal devices as secondary screen devices with the aim of identifying viewers and capturing their interactions with interactive TV devices. One important application for this data consists of generating personalized content for single viewers and groups of viewers.
\end{abstract}

@@

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information. After many advances in technologies, for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. In this scenario, the data generated by the interactions of millions of viewers can provide valuable information for content providers (CPs) to improve their services~\cite{Teixeira2010}.

The conventional remote control (RC) is typically used as the standard medium for viewers to interact with their TVs. However, this medium presents two notable problems: (1) to automatically identify the viewers who have possession of the RC; and (2) to capture contextualized viewers' interactions. As a result, the entire group of viewers (e.g., a family) is treated as a single viewer and the tastes that were inferred from the users in charge of the RC can be imposed on the tastes of the others.

Given the limitations of the conventional RC, a novel secondary screen architecture to identify viewers who are interacting with interactive TV (iTV) services is presented in this paper. Personal devices (e.g., smartphones and tablets) are used as secondary screens with the aim of capturing personal and contextualized interactions from each active viewer in iTV environments. By using proper machine learning algorithms, the personal data can reveal important information about viewers' tastes~\cite{Kim2012,Shin2009}.

@@

% In order to support millions of viewers, this architecture was implemented under a cloud computing based platform.

% Data about viewers' interactions are captured by personal devices (e.g., smartphones and tablets) that are used to mediate the interaction between viewers and the iTV device.

% \blurb{Achei que o inicio da introducao esta com muito bla bla bla. Tente ir direto ao ponto, dando uma visao geral da sua abordagem, as vantagens e desvantages com as outras abordagens existentes na literatura e as principais contribuicoes do seu trabalho. Por que voce acredita que os revisores devem aceitar o seu trabalho? Qual eh a inovacao? Quais sao as contribuicoes? Quais sao as diferencas para os trabalhos que ja existem. Diminua o bla bla bla do inicio e tente responder estas perguntas na introducao do seu trabalho.}

@@

The architecture to accurately capture viewers interactions is shown in~\figurename~\ref{fig_architecture}. This architecture consists of secondary screen devices, which might be implemented in personal devices such as smartphones and tablets, an iTV device, and the CP infrastructure, which includes an application hosting infrastructure. Since applications in the TV domain have the potential to reach out millions of users at the same time, it is interesting that the CP infrastructure has the ability to deal with a large amount of incoming data~\cite{Lee2010}. The dashed green arrows represent the data flowing from the viewer to the CP infrastructure, while dotted blue arrows denote the flow from CP infrastructure to the viewers. The continuous black arrows represent the data flow inside the CP infrastructure.

>>>>

\begin{abstract}
Advances in TV technology have enabled viewers to actively interact with the TV through interactive applications instead of just passively watching TV. Typically, a conventional remote control is shared by many viewers and it is difficult to accurately capture the individual interaction data from each viewer. It is also difficult to identify the context in which the interactions occur, e.g., to manage precisely who is present in the environment and what is being watched on TV. In this paper, it is presented a novel architecture that facilitates the capture of viewers' individual interactions and contextual data in shared TV environments. This architecture uses personal devices as secondary screen devices with the aim of identifying viewers and capturing their interactions with interactive TV devices. A work in progress implementation of this architecture is briefly reported as an audio-visual content rating system for interactive TV.
\end{abstract}

@@

TV watching is essentially a social activity, where groups of people with a common interest share the same space and TV set for entertainment or information. After many advances in technologies, for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. In this scenario, the data generated by the interactions of millions of viewers can provide valuable information for content providers (CPs) to improve their services~\cite{Teixeira2010}.

The conventional remote control (RC) is typically seen as the standard medium of interaction among the viewers and their TVs. However, this medium presents two notable problems: (1) to precisely and automatically identify the viewers who have possession of the RC; and (2) to capture contextualized viewers' interactions. As a result, the entire group of viewers (e.g., a family) is treated as a single viewer and the tastes that were inferred from the users in charge of the RC can be imposed on the tastes of the others.

Given the limitations of the conventional RC, a novel secondary screen architecture to identify viewers who are interacting with interactive TV (iTV) services is presented in this paper. Personal devices (e.g., smartphones and tablets) are used as secondary screens with the aim of capturing personal and contextualized interactions from each active viewer in iTV environments. By using proper machine learning algorithms, the personal and contextualized data can reveal important information about viewers' tastes~\cite{Kim2012,Shin2009}.

@@

@@

The architecture to precisely capture viewers interactions and the context is shown in~\figurename~\ref{fig_architecture}. This architecture consists of tree subsystems that interact with each other: (1) secondary screen devices, which might be implemented in personal devices; an (2) iTV device; and (3) the CP infrastructure, which includes an application hosting infrastructure. The dashed arrows represent the data flowing from the viewer to the CP infrastructure, while dotted arrows denote the flow from CP infrastructure to the viewers. The continuous arrows represent the data flow inside the CP infrastructure. Since applications in the TV domain have the potential to reach out millions of users at the same time, it is interesting to consider the use of a cloud based platform in the CP infrastructure~\cite{Lee2010}.
